Effectful Semantics for Substructural SSA

### 2023-11-13 pldi24/paper.tex
Blurbs about typing rules

@@

\TODO{some text about each block typing rule}

>>>>

The rules for block typing are given in Figure \ref{fig:ssa-block-typing}.
\rle{br} says that, given a pure term \(a: A\) which is \textit{both} affine and
relevant (i.e. intuitionistic), we can type a block \(\lbrb{\ell}{a}\) which
branches to \(\ell\) with argument \(a\), where \(\ms{L}\) contains the context
\(\ell\) with an argument type of \(A\) and an appropriate set of unused
variables. The rule \rle{ite} typechecks if-then-else statements by stating
that, if \(\Gamma\) splits into \(\Delta\) and \(\Xi\), where \(\Xi\) typechecks
a pure, intuitionistic discriminant \(e: \mb{2}\) and \(\Delta\) typechecks both
\(s, t\) to branch into \(\ms{L}\), then the whole if-statement
\(\ite{e}{s}{t}\) also typechecks as branching into \(\ms{L}\) in constext
\(\Gamma\). \rle{let-blk} and \rle{let2-blk} are quite similar to their
expression analogues, except that the bound expression \(e\) is allowed to be
impure (otherwise, programs could only make use of pure functions!), and the
remainder of the context plus the bound variable is used to type a block rather
than a term. Finally, probably the most interesting rule is \rle{where}, which
says that, given a block \(t\) which branches to \(\ms{L}\) in context
\(\Gamma\), and labels \(L\) mapping \(\ms{L}\) to \(\ms{K}\), \(\ewhere{t}{L}\)
branches to \(\ms{K}\). Here, \(L\) mapping \(\ms{L}\) to \(\ms{K}\) is defined
using the typing rules \rle{nil-br}, which says that an empty list of blocks
leaves the target label-set unchanged, and \rle{cons-br}, which says that if
\(L\) maps \(\ms{L}\) to either \(\ms{K}\) or the label
\(\lbl{\ell}[\Gamma](A)\), and \(t\) branches to \(\ms{L}\) in the context
\(\Gamma, \thyp{x}{A}{}\), then \(L\) maps \(\ms{L}\) to \(\ms{K}\), having
(potentially recursively) defined \(\lbl{\ell}\).

@@
